%-------------------------
% Resume in Latex
% Author : Glênio Borges
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{amsmath} % Include the amsmath package

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
%\newcommand{\resumeItem}[1]{
%  \item\small{
%    {#1 \vspace{-2pt}}
%  }
%}

\newcommand{\simpleItem}[1]{
  \item\small{
    \textnormal{#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}



%\newcommand{\resumeSubheading}[4]{
%  \vspace{-2pt}\item
%    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%      \textbf{#1} & #2 \\
%      \textit{\small#3} & \textit{\small #4} \\
%    \end{tabular*}\vspace{-7pt}
%}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


%\newcommand{\resumeSubSubheading}[2]{
%    \item
%    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
%      \textit{\small#1} & \textit{\small #2} \\
%    \end{tabular*}\vspace{-7pt}
%}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
%\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
%\newcommand{\resumeItemListStart}{\begin{itemize}}
%\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Glenio Borges} \\ \vspace{1pt}
    \small New York Metro Area $*$ 917-353-4673 $*$ \href{mailto:x@x.com}{\underline{glenioborges@gmail.com}} $*$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/dambor}} $*$
    \href{https://github.com/...}{\underline{github.com/dambor}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Platform Engineer}{ with 8+ years of expertise in crafting cloud-based platforms, containerized systems, and robust CI/CD pipelines. Proven track record of boosting developer efficiency, streamlining deployments, and ensuring high availability across AWS, GCP and Azure environments. Skilled collaborator with a passion for building scalable web applications and promoting best practices.}
    }}
  \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {VMware}{New York City, NY}
      {Engineering Lead}{Jan. 2020 -- Mar. 2024}
      \resumeItemListStart
        \simpleItem{Led a team of 20+ technical professionals in the development and delivery of a platform-as-a-Service (PaaS) for Kubernetes.}
        \simpleItem{Provided technical guidance and mentorship to team members, fostering a collaborative and innovative work environment.}
        \simpleItem{Managed project timelines, resources, and deliverables to ensure on-time and within-budget completion.}
        \simpleItem{Facilitated communication and collaboration between cross-functional teams, including engineering, product management, sales and marketing.}
        \simpleItem{Conducted performance evaluations and provided feedback to team members to support their professional growth and development.}
        \simpleItem{Implemented best practices, Continuous Integration and Delivery (CI/CD), and Agile methodologies to optimize team productivity and project efficiency.}
        
      \resumeItemListEnd

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
      
    \resumeSubheading
      {Pivotal}{New York City, NY}
      {Platform Architect}{Nov. 2018 -- Jan. 2020}


      \resumeItemListStart

        \simpleItem{Spearheaded the design and implementation of a Kubernetes-based infrastructure on AWS, reducing deployment times by 40\% and improving resource utilization.} 
        \simpleItem{Led the development of CI/CD pipelines using Jenkins, enabling frequent releases and enhancing code quality.}
        \simpleItem{Collaborated with multiple development teams to establish containerization standards, promoting consistency and efficient workflows.}
        \simpleItem{Built infrastructure-as-code solutions with Terraform, streamlining provisioning and management of cloud resources.}
        \simpleItem{Mentored junior engineers in best practices for cloud infrastructure and containerization.}

      

    \resumeItemListEnd

    \resumeSubheading
      {Pivotal}{São Paulo, Brazil}
      {Solutions Director}{Dec. 2015 -- Nov. 2018}


      \resumeItemListStart
        \simpleItem{Designed and implemented BigData solutions, ensuring scalability and performance within complex enterprise environments. }
        \simpleItem{Built a data-driven mobile digital banking platform, providing a personalized, integrated customer experience by leveraging digital intelligence based on big data and advanced analytics.}
        \simpleItem{Developed and maintained relationships with key clients, ensuring high levels of customer satisfaction and retention.}
       
       
    \resumeItemListEnd

    \resumeSubheading
      {Ericsson}{São Paulo, Brazil}
      {Technical Project Lead}{Jul. 2011 -- Dec. 2015}
    

      \resumeItemListStart
        \simpleItem{Established project plan baseline, defining scope, securing the necessary resources and plans and monitor all activities.}
        \simpleItem{Drove project execution, tracked project activities, monitored and handled changes, conflicts and critical issues.}
        \simpleItem{Handled customer and partner engagement, led customer relationship building confidence and trust, and ensured project progress arranging meetings and customer events.}
        
      \resumeItemListEnd   

    \resumeSubheading
      {Ericsson}{São Paulo, Brazil}
      {Solutions Architect}{Jun. 2007 -- Jul. 2011}


      \resumeItemListStart
        \simpleItem{Led customer presentations and engagement.}
        \simpleItem{Participated in C-Level discussions based on an end-to-end BSS/OSS implementation and integration.} 
        \simpleItem{Contributed to and create RFP responses, solution documents, questionnaires, customer presentations, and related documents.}
      \resumeItemListEnd   

    \resumeSubheading
      {Ericsson}{São Paulo, Brazil}
      {System Integrator}{Oct. 2006 -- Jun. 2007}

      
      \resumeItemListStart
        \simpleItem{Executed product configuration, integration and migration work.}
        \simpleItem{Performed operation, administration and troubleshooting.}
        \simpleItem{Prepared system test, module test and acceptance test.}

        
      \resumeItemListEnd   

    \resumeSubheading
      {Algar Telecom}{Uberlândia, Brazil}
      {Software Engineer}{Mar. 2003 -- Oct. 2006}
      
      \resumeItemListStart
        \simpleItem{Developed new business rules for filtering out of non billing-relevant call detail records}
        \simpleItem{Supported and maintained critical mission Billing Mediation systems}
        \simpleItem{Correlated different input sources call detail records}
        \simpleItem{Aggregated partial call detail records related to the same call}
        
      \resumeItemListEnd   

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{University of Texas} $|$ \emph{Masters, Artificial Intelligence}} {Austin, TX - cohort fall 2024}
    \resumeProjectHeading
      {\textbf{São Paulo University - USP} $|$ \emph{MBA, Strategic Management}} {São Paulo, Brazil - Mar. 2014 - May. 2016}    \resumeProjectHeading
      {\textbf{Pitágoras University} $|$ \emph{BSc, Information Systems}}{Uberlândia, Brazil - Jul. 2001 -- Jul. 2005}
    \resumeProjectHeading
      {\textbf{Federal University of Uberlândia} $|$ \emph{BA, Music Performance}}{Uberlândia, Brazil - Jul. 1999 -- Dec. 2003}  
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Shell, Python, Go, JavaScript, HTML/CSS} \\
     \textbf{Databse}{: Redis, MongoDB, Postgres, Oracle, MySQL, Gemfire, Greenplum} \\
     \textbf{Frameworks}{: Spring Boot, Spring Cloud} \\
     \textbf{DevOps Tools}{: Git (GitLab, GitHub), CloudFoundry, Tanzu, Kubernetes, Docker, ArgoCD} \\
     \textbf{Cloud Providers}{: GCP, AWS, Azure, vSphere} \\
     \textbf{Infrastructure as Code (IaC)}{: Terraform, BOSH} \\
     \textbf{Leadership}{: Career Management, Hiring, Team Building, Agile, Project Management}
    }}
 \end{itemize}

%-----------CERTIFICATES & AWARDS-----------

\section{Certificates}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Applied Data Science Program} $|$ \emph{Massachussets Institute of Technology}}{2023}
    \resumeProjectHeading
      {\textbf{CKAD: Certified Kubernetes Application Developer} $|$ \emph{Linux Foundation}}{2019}  
    \resumeProjectHeading
      {\textbf{Data Science Specialization} $|$ \emph{John Hopkins Bloomberg School of Public Health}}{2015}
    \resumeProjectHeading
      {\textbf{Tame Big Data for Big Insight} $|$ \emph{Stanford University}}{2015}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading    
      {\textbf{Developer Portal} $|$ \emph{TypeScript, Backstage.io, Postgres, Kubernetes, AWS}} {2023}  
    \resumeProjectHeading
      {\textbf{Learning Center} $|$ \emph{Python, Kubernetes, CRD, Operator, AWS}} {2020}
    \resumeProjectHeading
      {\textbf{Mission Control} $|$ \emph{Golang, ClusterAPI, JavaScript, AWS}} {2019}
    \resumeProjectHeading  
      {\textbf{Cloud Ridge} $|$ \emph{Spring Boot/Cloud, AWS, CloudFoundry, Jenkins}} {2018}
    \resumeProjectHeading
      {\textbf{Digital Bank} $|$ \emph{Python, Hadoop, Greenplum, Gemfire, MachineLearning, CloudFoundry, vSphere}} {2017}
    \resumeProjectHeading
      {\textbf{Fast Data} $|$ \emph{Spring Boot, Gemfire, CloudFoundry, vSphere}} {2016}
    \resumeProjectHeading
      {\textbf{Online Mediation} $|$ \emph{Java, WebService, SOA}} {2011}
  \resumeSubHeadingListEnd


\end{document}


